Relational Presentations Using Semantic Closeness\\Spatial Narrative for Mathematical Content

### 2015-06-16 Paper.tex
citation comment addressed
tweaks

\begin{abstract}
Visualization of knowledge is important to foster learning. Especially so in Mathematics where students have to understand not just one topic at a time but also the related concepts. Taking the typical Mathematics lecture as an example, it is often the case that students come from different backgrounds. When a new topic is introduced it would therefore be ideal to have a simple way to find dependencies and present students with an easy way to catch up on topics they have not learned. To optimize the visualization of information and its interdependencies, a way to present information without losing context is therefore necessary. The following research takes an existing annotated corpus and presents its contents while allowing students to see dependencies between topics and encouraging them to explore related mathematical concepts. Thus students can interactively learn the concepts the current topic depends on by taking small detours through those topics, should they need to refresh their memories. This approach to presenting learning materials changes how we interact with course materials and it is ultimately applicable to almost all areas in which knowledge needs to be transferred.
\end{abstract}

@@

\subsection{Status of Information within the (Dis)Course}
\label{sec:infostatus}
In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed. Within the study of \textit{information structure}, one discriminates between \textit{familiar/ old} and \textit{unfamiliar/ new} information. \textit{Familiar/ old} information is shared by speaker and addressee, i.e. it is in the intersection of knowledge of student and teacher. \textit{New/ unfamiliar} information is not in the shared knowledge base or the content commons \cite{CNX:whitepaper}. In addition, one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.

@@

\begin{figure}[ht]\vspace{-1.5em}
  \fbox{\includegraphics[width=1\textwidth]{assets/final/inclusionGraphPythagorean}} 
  \vspace{-1.5em}
  \caption{Pythagorean Theorem Inclusion Graph}\label{fig:inclusionGraph}
\vspace{-2em}
\end{figure}

@@

\begin{figure}[ht]\vspace{-1.5em}
  \fbox{\includegraphics[width=1\textwidth]{assets/final/fullPresentation2}} 
  \vspace{-1.5em}
  \caption{Visualization of Dependencies}\label{fig:visualDependency}
\vspace{-2em}
\end{figure}

>>>>

\begin{abstract}
  Visualization of knowledge is important to foster learning. Especially so in Mathematics
  where students have to understand not just the topic hand but also related concepts. It
  would therefore be ideal to have a simple way to find dependencies and present students
  with an easy way to catch up on topics they have not learned yet without losing
  context.

  Our research takes an existing annotated corpus and presents its contents while allowing
  students to see dependencies between topics and encouraging them to explore related
  mathematical concepts. Thus students can interactively learn the concepts the current
  topic depends on by taking small detours through those topics, should they need to
  refresh their memories. This approach to presenting learning materials changes how we
  interact with course materials and it is ultimately applicable to almost all areas in
  which knowledge needs to be transferred.
\end{abstract}

@@

\subsection{Status of Information within the (Dis)Course}
\label{sec:infostatus}
In linguistics the concept of information packaging \cite{CambridgeGrammar:npentrel14} is well known and widely discussed. Within the study of \textit{information structure}, one discriminates between \textit{familiar/ old} and \textit{unfamiliar/ new} information. \textit{Familiar/ old} information is shared by speaker and addressee, i.e. it is in the intersection of knowledge of student and teacher. \textit{New/ unfamiliar} information is not in the shared knowledge base. In addition, one distinguishes information that is old or new with respect to the discourse or with respect to the addressee.

@@

\begin{figure}[ht]\vspace{-1.5em}
  \fbox{\includegraphics[width=.97\textwidth]{assets/final/inclusionGraphPythagorean}} 
  \vspace{-.5em}
  \caption{Pythagorean Theorem Inclusion Graph}\label{fig:inclusionGraph}
\vspace{-2em}
\end{figure}

@@

\begin{figure}[ht]\vspace{-1.5em}
  \fbox{\includegraphics[width=.97\textwidth]{assets/final/fullPresentation2}} 
  \vspace{-.5em}
  \caption{Visualization of Dependencies}\label{fig:visualDependency}
\vspace{-2em}
\end{figure}
